\subsection{About the Authors}
%    \marginnote{please write a mini-biography/description of yourself, qualifications, and current work, and anything else you might think of :)}
\label{paper1:colophon}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%% START ACKNOWLEDGEMENTS.tex %%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Bagga Bjerge}, PhD, is Associate Professor at \textit{Centre for Alcohol and Drug Research}, Aarhus University. She is trained within anthropology and sociology. Her research activities are mainly based on qualitative methods focusing on policies and policy implementation, bureaucracy, social work as well as social marginalization. Currently, her research projects focus on poverty, drug scenes in Copenhagen, marginalized Greenlanders in Denmark and the management of citizens with complex cases.
\\
\textbf{Tobias Georg Eule}, PhD, is Professor of Sociology of Law in the \enquote{Department of Law}, University of Bern. His research interests include policy implementation, migration control, decision-making as well as anthropological and sociological theories of the state.
\\
\textbf{Kasper Trolle Elmholdt}, PhD, is an Assistant Professor of Organisation and Public Management in the \textit{Department of Political Science, Centre for Management, Organisation and Administration} (COMA), at Aalborg University, Denmark. His research interests include management consulting, the performativity of management theories and practice-based studies, which he typically explore through an ethnographic stance. 